\section{Scope and Limitations}
This section identifies what part of the envisioned solution is going to be
developed in this current project or version, what will be delayed until
latter projects, and what is out of scope for the whole product.  

\subsection{Scope of Initial Release}
For the initial release of our project, we would like to include all features discussed above in the Vision section for our initial release. Our Kiosk will be an interactive touchscreen that includes a map of the fourth floor CS department so that students will know where faculty offices are, and when faculty are available for meetings. The Kiosk will also display upcoming CS events when the Kiosk is not being used. 

\subsection{Scope of Subsequent Releases}
In subsequent releases, we would like to include the ability to schedule a meeting with a CS faculty member directly through the Kiosk. We would potentially like to extend our map of the fourth floor CS department to include other floors of the Communications Facility. Additionally, for subsequent releases we would like to include student software demos through our Kiosk so we can feature new and creative ideas from the CS students. 

\subsection{Limitations and Exclusions}
Through our project release and any other subsequent releases, there are certain features that we have deemed out of scope for the Kiosk. We do not ever plan for the Kiosk to have the ability to make calls directly to faculty members. Our Kiosk will not have the ability for students to enter their own events, only CS approved events and clubs will be displayed through the Kiosk. 

